\documentclass[11pt,oneside]{article}
\usepackage[english]{babel}
\usepackage[top=5pt,bottom=5pt,left=1.7cm,right=1.7cm,a4paper]{geometry}
\usepackage{calc}
\usepackage{tikz,pgf}
\usetikzlibrary{shapes,shadows}
\usepackage[english]{babel}
\usetikzlibrary{backgrounds}
\usepackage[hidelinks=true,linkcolor = blue,breaklinks=true]{hyperref}
\usepackage{color}
\usepackage{array}
\usepackage{graphics}
\usepackage{titlesec}
% fonts
\usepackage{fontawesome5}
\usepackage{academicons}

\usepackage[sfdefault]{ClearSans}

% page style
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\parindent=0pt

% Top banner background
\colorlet{banerColor}{gray!10}
\definecolor{SwishLineColour}{HTML}{007ae0}

\newcommand{\drawBaner}{%
	\begin{tikzpicture}[remember picture, overlay]
		\fill[banerColor] (-50pt,30pt) rectangle (\paperwidth,-0.127\paperheight);
	\end{tikzpicture}%
}
\newcommand{\liner}{\begin{tikzpicture}[remember picture,overlay]%\
		\fill[left color=cyan, right color=white,white] (0,-2pt) rectangle (\linewidth,-3.5pt);
		\end{tikzpicture}}
%\titleformat{command}[shape]{format}{label}{sep}{before-code}[after-code]
\titleformat{\section}[display]{\Large\bfseries}{}{0pt}{\liner}[\vspace*{-5pt}]

\newcommand{\slink}[1]{\underline{\smash{\color{cyan}#1}}}
\newcommand{\link}[1]{\href{#1}{\color{cyan}\faGlobe}}



\newcommand{\cvInfo}[2]{\makebox[1em]{\color{black}#1} \color{black}#2\hspace*{1em}\vspace*{5pt}}



\newcommand{\cvEduc}[3]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\arraybackslash}p{\linewidth}}
		#1 & \textbf{#2}  \\
		&#3 \\
\end{tabular}}



\newcommand{\cvWP}[4]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{8cm}>{\raggedleft\arraybackslash}p{\linewidth-2.5cm}}%
		#1 & \textbf{#2} & \textbf{#3}\\%
		&\multicolumn{2}{>{\arraybackslash}p{\linewidth - 3.2cm}}{#4}\\%
\end{tabular}}

\newcommand{\cvWPA}[3]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13cm}}%
		#1 & \textbf{#2}\\%
		&#3\\%
\end{tabular}}



\newcommand{\cvitem}[2]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13cm}}
		\textbf{#1} & #2  \\
\end{tabular}}

\newcommand{\cvitemi}[2]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13cm}}
		#1 & #2  \\
	\end{tabular}}





\newcommand{\header}{
	\newpage
	\vspace*{15pt}
	\begin{tikzpicture}[remember picture,overlay]%\
		\node at (-5pt,0) [right] {Jean Lucien RANDRIANANTENAINA};
		\node at (\linewidth,0) [left]{Curriculum Vitae};
		\fill[left color=gray,right color=gray,white] (0,-5pt) rectangle (\linewidth,-6pt);
\end{tikzpicture}
\vspace*{15pt}}

\newcommand{\cvRefTitle}[2]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13cm}}
		& \textbf{#1} $|$ \textbf{#2}  \\
\end{tabular}}

\newcommand{\cvRefEntry}[1]{\begin{tabular}{>{\raggedleft\arraybackslash}p{2.5cm}>{\raggedright\arraybackslash}p{13cm}}
		& #1 \\
\end{tabular}}

\title{Curriculum Vitae}
\author{Jean Lucien RANDRIANANTENAINA}


\begin{document}
\drawBaner

\begin{minipage}{\linewidth}
	\begin{center}
		{\bfseries
		\Large Jean Lucien Randrianantenaina - Mathematician / Python developer}
	\end{center}
	\hfill\begin{minipage}{0.57\linewidth}
		\cvInfo{\faUser}{Born 3\textsuperscript{rd} of April 1998, Madagascar}

		\cvInfo{\faHome}{Lot 03A/BA Beravina Fianarantsoa Madagascar}

		\cvInfo{\faHome}{P.O BOX  608, Crystal Gardens, Limbe Cameroon}

		\cvInfo{\faEnvelope}{\slink{\href{lucien.randrianantenaina@aims-cameroon.org}{\slink{lucien.randrianantenaina@aims-cameroon.org}}}}
	\end{minipage}\begin{minipage}{0.47\linewidth}
		\cvInfo{\faPhone}{\ttfamily+237 693 796 760 / +261 345 898 164}

		\cvInfo{\faGithub}{\slink{\href{https://github.com/Fahazavana}{\slink{Fahazavana}}}}

		\cvInfo{\faLinkedin}
		{\slink{\href{https://www.linkedin.com/in/randrianantenaina-jean-lucien-82b98622b/}{\slink{Jean Lucien RANDRIANANTENAINA}}}}

		\cvInfo{\faEnvelope}{\slink{\href{mailto:rjlucienaina@gmail.com}{\slink{rjlucienaina@gmail.com}}}}
	\end{minipage}\hfill
\end{minipage}
 
\vspace*{7pt}
{\small Notes : {\color{cyan}\faGlobe} denote a web hyperlink.}
\vspace*{-10pt}

\section{Summary}
I am a mathematics student with a primary interest in algebra, combinatorics, number theory, and cryptography. I am also a self-taught Python programmer and web developer (back-end) with a strong interest in Artificial Intelligence and Data Science. These two domains complement each other, and I like to learn and explore new horizons in research for innovative solutions. I am motivated, dynamic, creative and ready to face problems and obstacles.
\section{Education}
\cvEduc{2022 -- 2023}{Structured Master, Fundamental Science Stream}{African Institute for Mathematical Sciences Cameroon.}


\vspace*{5pt}
\cvEduc{2018 -- 2022}{Master 2, in Fundamental Mathematics}{Faculty of Science, University of Fianarantsoa, Madagascar.\newline All modules completed, but program interrupted due to external circumstances.}
%

\vspace*{5pt}
\cvEduc{2015 -- 2018}{Bachelor Degree, in Fundamental Mathematics}{Faculty of Science, University of Fianarantsoa, Madagascar.\newline
Project : ``Resolution Par Radicaux'', Supervised by Pr. Solo Randriamahaleo.}
% 

\vspace*{5pt}
\cvEduc{2014 -- 2015}{Baccalaureate, in Technology in Industrial Engineering}{Technical High School Beravina Fianarantsoa, Madagascar.}

\section{Academic Projects and Talks}
\cvWPA{Currently}{AIMS research essay: ``Carmichael number of the form $2^np^2+1$ and $2^np^3+1$''.}{Supervised by Prof. Florian Luca, University of Witwatersrand, South Africa.}
%

\vspace*{5pt}
\cvWPA{2023}{AIMS talk : ``Fermat last theorem, with n=4'' \link{https://drive.google.com/file/d/1NQMheu7RrMmY6wJM9X-6aasbnj1nnsfF/view?usp=share_link}}{Presented to AIMS Cameroon students. Supervised by Prof. Dr Hans Georg Ruck, Universität Kassel.}
%
\section{Personal Projects}
%
\cvWP{Currently}{Mk-Forum \link{https://github.com/Fahazavana/MK-Forum}}{}{Creation of a forum dedicated to Mathematics with HTML, CSS/Bootstrap, JS for the Front-end and Python3/Django, MySQL for the Back-End.}
%

\vspace*{5pt}
\cvWP{2023}{FCryptos \link{https://github.com/Fahazavana/FCryptos} }{}{Implementation of cryptography methods with Python : Shift cipher, Vin\`egre cipher, SPN, RSA, ENIGMA machine.}
%

\vspace*{5pt}
\cvWP{2022}{Pendu Malagasy \link{https://github.com/Fahazavana/Pendu\_Malagasy}}{}{A Malagasy version of the game hangman, built with Python3/TKinter.}


\header


\vspace*{5pt}
\cvWP{2022}{Unbeatable TicTacToe \link{https://github.com/Fahazavana/SAYNA-JAVASCRIPT-MORPION-042022}}{}{Tic-Tac-Toe created  with HTML, CSS and JavaScript, and features an automated computer player that uses a combination of random placement and min-max algorithm to make each move depending on the chosen level.}%Using random placement and min-max algorithm to automate the move of the .}
%

\vspace*{5pt}
\cvWP{2019}{Bellman-Kalaba \link{https://github.com/Fahazavana/Bellma-Kalaba} }{}{A graphical interface for the algorithm of Bellman-Kalaba (shortest-path) made with Python3/TKinter.}
%


\section{Extracurricular Courses}
\cvWP{Jan.-Jul. 2022}{Back-End Web Development \link{https://drive.google.com/file/d/1hZAeH4\_e4YTLU4y1wLXLXMY7XCZfVE5-/view?usp=sharing}}{SAYNA academy (D-CLIC program)}{Html, CSS, JavaScript, MySQL and Node.Js.}

\vspace*{5pt}
\cvEduc{2021}{CIMPA Research school Fianarantsoa Madagascar}{Probabilistic and statistical modelling in epidemiology and environment.}%

\section{Skills}
\cvitem{Languages}{English (advanced), French (advanced), Malagasy (native).}%{Malagasy as mother tongue, with an academic English level of writing and speaking. Good in French Writing and speaking}

\vspace*{5pt}
\cvitem{Coding}{PHP, Python, R, SQL, \LaTeX, SageMath, Pascal, Prolog.}

\vspace*{5pt}
\cvitem{Databases}{MySQL, SQLite.}


\section{Extra Academic Involvement and Interest}
\cvitemi{2023}{Group leader mentoring children in S.T.E.M., Saker baptist school Limb\'e Cameroon.}

\vspace*{5pt}
\cvitemi{2022}{Certificate In Communication, Self-awareness, Mental strength, Choosing a positive attitude, delivered by \textbf{Hello Elton}.}

\vspace*{5pt}
\cvitem{Other}{Music (singing, playing guitar), Trekking, football.}


\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvRefTitle{Prof. Florian Luca}{Professor of Number Theory}

\cvRefEntry{Department of Mathematics}

\cvRefEntry{University of the Witwatersrand, South Africa}

\cvRefEntry{Phone : +270 117 176 243}

\cvRefEntry{Email: \href{mailto:Florian.Luca@wits.ac.za}{\color{cyan}\underline{Florian.Luca@wits.ac.za}}}


\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvRefTitle{Prof. Andreas Buchleitner}{Professor of Theoretical Physics}

\cvRefEntry{Department for Quantum Optics and Statistics}

\cvRefEntry{Institute of Physics, Albert-Ludwigs-Universität Freiburg}

\cvRefEntry{Hermann-Herder-Str. 3, D-79104 Freiburg}

\cvRefEntry{Phone: +49 761 203 5830}

%\cvRefEntry{Fax: +49 761 203 5967}

\cvRefEntry{Email: \href{mailto:a.buchleitner@physik.uni-freiburg.de}{\color{cyan}\underline{a.buchleitner@physik.uni-freiburg.de}}}


\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvRefTitle{Prof. Solo Randriamahaleo Rajaofetra}{Professor of Algebra}

\cvRefEntry{Department of Mathematics and Applications}

\cvRefEntry{Faculty of Sciences, University of Fianarantsoa, Madagascar}

\cvRefEntry{Lotissement 33, Ambatotsidikaina, Fianarantsoa}

\cvRefEntry{Phone : +261 34 01 226 31}

\cvRefEntry{Email: \href{mailto:solo.randriamahaleo@gmail.com}{\color{cyan}\underline{solo.randriamahaleo@gmail.com}}}


\end{document}
